### 2019-06-03 Intro.Rmd
abstract

---
output:
  bookdown::pdf_document2:
    keep_tex: yes
    toc: false
textalign: left  # this does not work...
geometry: margin = 1in
bibliography: library_red.bib
csl: systematic-biology.csl
link-citations: yes
linestretch: 2
header-includes:
    - \usepackage[left]{lineno}
    - \linenumbers
nocite: |
  @barker2012going, @barker2015new, @burns2014phylogenetics, @claramunt2015new, @gibb2015new, @Hedges2015, @hooper2017chromosomal, @Jetz2012, @price2014niche
---

>>>>

---
output:
  bookdown::pdf_document2:
    keep_tex: yes
    toc: false
textalign: left  # this does not work...
geometry: margin = 1in
bibliography: library_red.bib
csl: systematic-biology.csl
link-citations: yes
linestretch: 2
header-includes:
    - \usepackage[left]{lineno}
    - \linenumbers
nocite: |
  @barker2012going, @barker2015new, @burns2014phylogenetics, @claramunt2015new, @gibb2015new, @Hedges2015, @hooper2017chromosomal, @Jetz2012, @price2014niche
---
`datelife`'s database includes all chronograms derived from expert knowledge, and this includes those derived from secondary calibrations.

Improvements:
* fossils as calibrations: Using secondary calibrations can generate biased ages when using bayesian methods, mainly because we don't know what prior to give to secondary calibrations
[@Schenk2016].
* bayesian congruification
* topological congruification
